%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \documentclass[]{deedy-resume-openfont}
  
      \begin{document}
      
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %
  %     Profile
  %
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  
\namesection{Dheeraj} {Lalwani}\infoline{\href{mailto:lalwanidheeraj1234@gmail.com}{lalwanidheeraj1234@gmail.com} | +91 8451904417 \\\vspace{4pt}\linksline{\descript{\href{https://github.com/dheerajdlalwani}{GitHub | }}\descript{\href{https://linkedin.com/in/lalwanidheeraj}{Linkedin | }}\descript{\href{https://twitter.com/DhiruCodes}{Twitter}}}\underlineheader{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Education
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\raggedright

    \runsubsection{Thadomal Shahani Engineering College (TSEC), Mumbai}\hspace*{\fill}  \location{August 2019 - May 2023}\\
    \descript{Bachelors Computer Engineering}\hspace*{\fill}\location{Mumbai}\
    CGPA: 9.402\\
    \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Experience
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\runsubsection{Riggle}\descript{| Backend Engineering Intern}\hfill \location{Mumbai, India | June 2022 – Present}
    \begin{tightemize}
        \item Built RESTFul APIs from scratch for a suite of six interconnected Supply Chain Products which are consumed by Web and Mobile Applications.
        \item Stack: Python, MySQL, Django, Django REST Framework.
    \end{tightemize}
\sectionsep
\runsubsection{Navlakhi}\descript{| Intern}\hfill \location{Mumbai, India | June 2020 – August 2020}
    \begin{tightemize}
        \item Led a team of eight developers to build two internal platforms— student data management and to automate aggregation of data from CSV files to MySQL database.
        \item Stack: PHP, MySQL, HTML, CSS
    \end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\raggedright
\begin{tabular}{p{5cm}p{13.5cm}}
\descript{Programming Languages} & {\location{Python, Go, Java, PHP and JavaScript}} \\
\descript{Libraries/Frameworks} & {\location{Django, Django REST Framework, Flask, MySQL and SQLite}} \\
\descript{Miscellaneous} & {\location{Git, GitHub, Figma and Unit Testing}}
\end{tabular}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Projects
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects / Open-Source}
\raggedright
\runsubsection{\large{Dekho}} \descript{| \href{https://github.com/Chirag-And-Dheeraj/video-streaming-server}{Link}}\hfill \location{Go, FFMPEG, HTML, CSS, JS}\\
            \begin{tightemize}
  \item Dekho is a basic video streaming server written without using any 3rd party libraries.
  \item Applied the fundamentals HTTP Live Streaming \& chunked file uploads for large files.
\end{tightemize}
            \sectionsep
          
        
            \runsubsection{\large{Back to Work}}
            \descript{| \href{https://github.com/dheerajdlalwani/back-to-work}{Link}}\hfill \location{JavaScript, Chromium Web Extension APIs, HTML, CSS}\\
            \begin{tightemize}
  \item A web extension which attempts to keep you focused by blocking websites causing distraction.
\end{tightemize}
            \sectionsep
          
        
            \runsubsection{\large{Kata}}
            \descript{| \href{https://github.com/dheerajdlalwani/url-shortener}{Link}}\hfill \location{Flask, Python, MongoDB, JavaScript}\\
            \begin{tightemize}
  \item Kata is a simple, bare bones URL Shortener.
  \item Features: Shorten links anonymously, custom slugs and view click count.
  \item Goal with this project was to become comfortable learning new technologies on the fly.
\end{tightemize}
            \sectionsep
          
        
            \runsubsection{\large{Navidrome}}
            \descript{| \href{https://github.com/navidrome/navidrome/pull/1379}{Link}}\hfill \location{Go, Ginkgo, Gomega}\\
            \begin{tightemize}
  \item This is was originally a GSoC project but since it wasn\textquotesingle{}t opted by anyone, I chose to take it up.
  \item Implemented an API to fetch and display Lyrics of a particular song and also wrote unit tests.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Community Work
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Community Work}
\raggedright
        \runsubsection{\large{OTC (Our Tech Community)}}\descript{| Admin}\hfill \location{January 2020 - present}\\
    \begin{tightemize}
        \item Hosted over 500 hours of weekly \descript{\href{https://catchup.ourtech.community}{OTC CatchUp}} sessions since Oct 2020 involving technical discussion, project showcases and talks and organized \descript{\href{https://meetup.ourtech.community}{OTC MeetUp}} with over 60+ attendees.
        \item \descript{\href{https://ourtech.community}{Our Tech Community - Website}}
    \end{tightemize}
            \sectionsep
        \runsubsection{\large{TSEC CodeCell}}\descript{| Senior Committee Member}\hfill \location{July 2020 - present}\\
        \begin{tightemize}
        \item Organized 3 flagship hackathons - TSEC Hacks\textquotesingle{}21, 22 and 23 and organized workshops.
        \item Co-ordinated with over 25 senior and junior committee members.
    \end{tightemize}
\end{document}